---
title: "SWORK 881 week02"
author: "your name goes here "
date: "MM/DD/YYYY"
output: html_document
---

# load libraries
```{r setup, include=FALSE}

```


# Data
```{r}
# load data
give_your_data_name_here<- read_csv("")

#how many observations and variables? 

```
#how many observations and variables? 
[provide your answer here]


```{r}
# create a new variable called `depression` by summing all ptsd variables. Use tidy approach


```


```{r}
#run simple descriptive statistics for all variables


```

DESCRIBE THE DATA BRIEFLY HERE
[provide your answer here]



# Model and Visualization
> What is the effect of `age`, `sex`, and `education` on `depression score`? 

Create a linear regression model that answers the question above. Print the results of the output and model diagnostics.

```{r}
# lm

```


```{r}
# model diagnostics


```


```{r}
# use ggplot to plot histogram of residuals (use 20 bins)


```

# Discussion of Results

Describe and interpret your results, including any statistical information you believe important: 

